Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-25 experiement.tex
discussion and conclusion

\section{the experiment}
This works focuses on comparing the different miss use models to a reference
calculation in which a single large cascade is build and designed to directly
produce \gls{HEU} from natural uranium.
This works uses the Cyclus fuel cycle simulator to allow material exchange
between facilities.

@@

>>>>

\section{The experiment}
This works focuses on comparing the different miss use models to a reference
calculation in which a single large cascade is build and designed to directly
produce \gls{HEU} from natural uranium.
This works uses the Cyclus fuel cycle simulator to allow material exchange
between facilities.

@@

\subsection{Timestep effect}

As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
\ref{fig:case3}, the different cascade levels required up to $2n+1$, with $n$ the
level number to start enriching uranium. This corresponds to the time required
for the material to propagate from the natural uranium source to the level,
regardless of the duration of the timestep (hour, day, month,...). This is also
true for the number of timestep required to reach the equilibrium assays value in
the tail reprocessing cases. This is why one will only consider equilibrium
values.

### 2018-05-25 results.tex
discussion and conclusion

\section{Results}
As it can be observed on Figures \ref{fig:case1}, \ref{fig:case2} and
\ref{fig:case3}, the different cascade levels required up to $2n+1$, with $n$ the
level number to start enriching uranium. This corresponds to the time required
for the material to propagate from the natural uranium source to the level,
regardless of the duration of the timestep (hour, day, month,...). This is also
true for the number of timestep required to reach the equilibrium assays value in
the tail reprocessing cases. This is why one will only consider equilibrium
values.

@@

Model       &        &           & A         & A         & B         & B       & C         & C          \\
Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{NR_case1}
        \caption{No tail recycling}
        \label{sfig:case1_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{R_case1}
        \caption{Tail recycling}
        \label{sfig:case1_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model A, with (right) and without recycling (left).}
    \label{fig:case1}
\end{figure}

\subsection{Miss-use modeling}
As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
don't have the same effect on the cascade behavior. While the models A and C,
allow a quick enrichment gain, when the chaining the enrichment cascades, respectively
4/23/78/98 and 4/23/82/99, with model B, the enrichment gain is slower only
4/21/61/90...
The same effect is observed when recycling the tails\ldots

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{NR_case2}
        \caption{No tail recycling}
        \label{sfig:case2_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{R_case2}
        \caption{Tail recycling}
        \label{sfig:case2_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model B, with (right) and without recycling (left).}
    \label{fig:case2}
\end{figure}

\subsection{Tails recycling}
As demonstrated on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
\ref{sfig:case3_R}, recycling the tails increases the overall product assay at all
the different levels. As shown on Table \ref{tab:level}, the tail assay of level
$n$ is always higher than the product assay of level $n-2$, recycling the tails
of level $n$ will consequently increase the feed assay of level $n-1$. Moreover,
as the feed assay of level $n-1$ increases, its tail and product assays increase as well,
increasing de facto the feed assays of respectively cascade levels $n-2$ and $n$...
This effect allow to reduce the number of cascade levels required to reach
\gls{HEU} in case A and C.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{NR_case3}
        \caption{No tail recycling}
        \label{sfig:case3_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.18]{R_case3}
        \caption{Tail recycling}
        \label{sfig:case3_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model C, with (right) and without recycling (left).}
    \label{fig:case3}
\end{figure}

\subsection{\gls{HEU} Production}
As shown Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
$17$ to $38$ kg/y with the model B. For the reference calculation where all the
available cascades are used within a single large cascade design for direct
\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.

>>>>

\section{Results}

\subsection{Miss-use modeling}

@@

Model       &        &           & A/NR      & A/R       & B/NR      & B/R      & C/NR       & C/R          \\
%Recycling   &        &           & No        & yes       & No        & Yes     & No        & yes        \\
\midrule                                                                                                 
        &            & Feed      & $0.71w\%$ & $1.3w\%$  & $0.71w\%$ & $0.94w\%$ & $0.71w\%$ & $1.66w\%$ \\
Level 0 & Assay      & Product   & $4.13w\%$ & $7.7w\%$  & $4.13w\%$ & $5.43w\%$ & $4.13w\%$ & $9.53w\%$ \\
        &            & Tail      & $0.29w\%$ & $0.5w\%$  & $0.29w\%$ & $0.39w\%$ & $0.29w\%$ & $0.69w\%$  \\
        & Cascades   &           & 26.73     & 26.45     & 26.6      & 25.8      & 26.73     & 26.45      \\
\midrule                                                                                                 
        &            & Feed      & $4.13w\%$ & $11.9w\%$ & $4.13w\%$ & $6.84w\%$ & $4.13w\%$ & $13.0w\%$ \\
Level 1 & Assay      & Product   & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $30.7w\%$ & $22.9w\%$ & $69.8w\%$ \\
        &            & Tail      & $1.8w\%$  & $6.6w\%$  & $1.72w\%$ & $2.91w\%$ & $1.81w\%$ & $9.43w\%$  \\
        & Cascades   &           & 2.92       & 3.20      & 2.91      & 3.41     & 2.92      & 3.20       \\
\midrule                                                                                                 
        &            & Feed      & $22.8w\%$ & $55.7w\%$ & $20.6w\%$ & $34.3w\%$ & $22.9w\%$ & $72.6w\%$ \\
Level 2 & Assay      & Product   & $78.5w\%$ & $95.0w\%$ & $61.0w\%$ & $75.8w\%$ & $82.0w\%$ & $98.4w\%$ \\
        &            & Tail      & $4.12w\%$ & $50.9w\%$ & $9.56w\%$ & $17.5w\%$ & $15.7w\%$ & $69.4w\%$ \\
        & Cascades   &           & 0.31      & 0.35      & 0.37      & 0.64      & 0.32      & 0.35      \\
\midrule                                                                                                 
        &            & Feed      & $78.5w\%$ & N.A.      & $61.0w\%$ & $75.8w\%$ & $82.3w\%$ & N.A.      \\
Level 3 & Assay      & Product   & $98.2w\%$ & N.A.      & $90.4w\%$ & $95.0w\%$ & $99.1w\%$ & N.A.      \\
        &            & Tail      & $76.1w\%$ & N.A.      & $79.3w\%$ & $56.1w\%$ & $80.3w\%$ & N.A.      \\
        & Cascades   &           & 0.03      & N.A.      & 0.080     & 0.18      & 0.03      & N.A.      \\
\bottomrule
\end{tabular}
  \label{tab:level}
\end{table}

As illustrated on Figures \ref{sfig:case1_NR}, \ref{sfig:case2_NR} and
\ref{sfig:case3_NR} and summarized on Tab \ref{tab:level}, the different model
don't have the same effect on the cascade behavior. While the models A and C,
allow a quick enrichment gain, with the cascades chaining, respectively
4/23/78/98 and 4/23/82/99, the model B, the enrichment gain is only
4/21/61/90...  The same effect is observed when recycling the tails\ldots

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case1}
        \caption{No tail recycling}
        \label{sfig:case1_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case1}
        \caption{Tail recycling}
        \label{sfig:case1_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model A, with (right) and without recycling (left).}
    \label{fig:case1}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case2}
        \caption{No tail recycling}
        \label{sfig:case2_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case2}
        \caption{Tail recycling}
        \label{sfig:case2_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model B, with (right) and without recycling (left).}
    \label{fig:case2}
\end{figure}

\subsection{Tails recycling}

As demonstrated on Figures \ref{sfig:case1_R}, \ref{sfig:case2_R} and
\ref{sfig:case3_R}, recycling the tails increases the overall product assay at
all the different levels. As shown on Table \ref{tab:level}, the tail assay of
level $n$ is always higher than the product assay of level $n-2$, recycling the
tails of level $n$ will consequently increase the feed assay of level $n-1$.
Moreover, as the feed assay of level $n-1$ increases, its tail and product
assays increase as well, increasing de facto the feed assays of respectively
cascade levels $n-2$ and $n$...  This effect allow to reduce the number of
cascade levels required to reach \gls{HEU} in case A and C.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{NR_case3}
        \caption{No tail recycling}
        \label{sfig:case3_NR}
    \end{subfigure}%
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[scale=0.17]{R_case3}
        \caption{Tail recycling}
        \label{sfig:case3_R}
    \end{subfigure}
    \caption{Evolution of the product assays at each level with considering
    miss-use model C, with (right) and without recycling (left).}
    \label{fig:case3}
\end{figure}

\subsection{\gls{HEU} Production}

As shown Figure \ref{fig:HEU_rate}, recycling increases the final \gls{HEU}
production rate, from $2$ to almost $20$ kg/y when using model A and C, and from
$17$ to $38$ kg/y with the model B. For the reference calculation where all the
available cascades are used within a single large cascade design for direct
\gls{HEU} production, the \gls{HEU} production rate is slightly over $50$ kg/y.
